Fig1

### 2020-05-06 analysis/02_DESeq2.Rmd
new fig 2b
now with total sex differenes

```{r PRL}
PRLdata <- read_csv("../results/PRLvsd.csv")

@@

plot_grid(ab, c, nrow = 1, rel_widths = c(2,1.2), labels = c(" ", "d"), label_size = 12)

head(sexPRLdesg)

PRLhi <- sexPRLdesg %>%
  filter(direction.y == "hi")
PRLhi

PRLwgcna <- read_csv("../results/08_PRL_associated.csv") %>%
  dplyr::rename("gene" =  "x") %>%
  mutate(wgcna = "yes")
PRLwgcna

PRLwgcnaDEGs <- left_join(PRLwgcna, sexPRLdesg) %>%
  select(-direction.x) %>%
  dplyr::rename("PRL" =  "direction.y") 
PRLwgcnaDEGs %>%
  group_by(wgcna, PRL) %>%
  summarize(n = n())
head(PRLwgcnaDEGs)
# 90 of the 98 genes in the wgcna module are also DEGs, with increase expression in hi PRL
```

@@

```{r}
# label each bird with weather or not their pituitary had hi PRL or not
# then make new column with nest, eggs, or chicks, drop controls

@@

@@

>>>>

```{r PRL, eval = F}
PRLdata <- read_csv("../results/PRLvsd.csv")

@@

plot_grid(ab, c, nrow = 1, rel_widths = c(2,1.2), labels = c(" ", "d"), label_size = 12)
```

@@

```{r, eval = F}
# label each bird with weather or not their pituitary had hi PRL or not
# then make new column with nest, eggs, or chicks, drop controls

@@

colDatahypothesis %>%
  filter(tissue == "pituitary")  %>%
  group_by(sex, tissue, hiloPRL, treatment) %>%
  summarize(n = n())

@@

## tissue and sex differences

```{r}

for(i in "gonad"){

  newcolData <- subsetcolData4(colData, i)
  print(head(newcolData))
  # save counts that match colData
  savecols <- as.character(newcolData$V1) 
  savecols <- as.vector(savecols)

  dds <- DESeqDataSetFromMatrix(countData = newcountData,
                                colData = newcolData,
                                design = ~ sex )

  dds <- dds[rowSums(counts(dds) > 1) >= 10]  # filter more than sample with less 0 counts
  print(dds)
  print(dim(dds))
  dds <- DESeq(dds, parallel = TRUE) # Differential expression analysis

  myfilename = paste0("../results/DEseq2/sex/", i, "_vsd.csv")
  write.csv(vsd, myfilename)

  print(head(vsd))

  # save differential gene expression results
  sex <- createDEGdfsavesex("male", "female", i)
}

### 2020-05-06 analysis/figure-1.Rmd
rm whitespace
now with total sex differenes

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(Rtsne)

library(kableExtra) 
library(ggtext) # for italic fonts

@@

allDEG$tissue <- factor(allDEG$tissue , levels = tissuelevel)
allDEG$comparison <- factor(allDEG$comparison , levels = comparisonlevels)
allDEG$direction <- factor(allDEG$direction, levels = charlevels)
```

@@

```{r fig1, fig.width=7.25, fig.height=7.25}
a <- png::readPNG("../figures/images/fig_fig1b.png")
a <- ggdraw() +  draw_image(a, scale = 1)

b <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = " ", subtitle = "~ tissue * sex")    
c <- plottsneelipse(ftsne, ftsne$tissue, allcolors ) + labs(y = " ", subtitle = "~ tissue, females only")
d <- plottsneelipse(mtsne, mtsne$tissue, allcolors ) + labs(y = " ", subtitle = "~ tissue, males only")

abcd <- plot_grid(a,b,c,d, nrow = 1, labels = c("A", "B", "C", "D"), label_size = 8 )

e <- png::readPNG("../figures/images/fig_fig1a.png")
e <- ggdraw() +  draw_image(e, scale = 1)

f <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + 
  labs(x = NULL, subtitle = "hypothalamus")  + 
  facet_wrap(~sex, scales = "free")

h <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + 
  labs(x = NULL, subtitle = "pituitary") + 
  facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank())

j <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + 
   facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank()) +
  labs(x = "tSNE1 \n \n \n \n", subtitle = "gonads")

fhj <- plot_grid(f,h,j, nrow = 3, rel_heights = c(1,1,1.4),
                 labels = c("F", "H", "J"), label_size = 8)

# hyp
g <- makebargraph("hypothalamus","DEGs", 0, 4300) + 
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank())  +
  labs(subtitle = "hypothalamus")
# pit
i <- makebargraph("pituitary","DEGs", 0, 4300)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  +
  labs(subtitle = "pituitary")
# gon
k <- makebargraph("gonad","DEGs", 0, 4300) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabels)+
  labs(subtitle = "gonads")

gik <- plot_grid(g,i,k, nrow = 3, rel_heights = c(1,1,1.4),
                 labels = c("G", "I", "K"), label_size = 8)

fhjgik <- plot_grid(fhj, gik, nrow = 1, align = "h", rel_widths = c(1.5,2))

fig1 <- plot_grid(abcd, e, fhjgik, nrow = 3, rel_heights = c(0.7,0.5,1.5),
                  labels = c(" ","E"), label_size = 8 )
fig1
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(Rtsne)
library(kableExtra) 
library(ggtext) # for italic fonts

@@

allDEG$tissue <- factor(allDEG$tissue , levels = tissuelevel)
allDEG$comparison <- factor(allDEG$comparison , levels = comparisonlevels)
allDEG$direction <- factor(allDEG$direction, levels = charlevels)

hypsex <- read_csv("../results/DEseq2/sex/hypothalamus_female_male_DEGs.csv")
pitsex <- read_csv("../results/DEseq2/sex/pituitary_female_male_DEGs.csv")
gonsex <- read_csv("../results/DEseq2/sex/gonad_female_male_DEGs.csv")

```

@@

```{r fig1, fig.width=7.25, fig.height=7.25}

a <- png::readPNG("../figures/images/fig_fig1a.png")
a <- ggdraw() +  draw_image(a, scale = 1)

b <- plottsneelipse(chartsne, chartsne$tissue, allcolors)   + labs(y = "tSNE 2 ", subtitle = " ")  
c <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = "tSNE 2 ", subtitle = " ")

d1 <- sexbarplots(hypsex, 0, 7000) + labs(y = "DEGS", subtitle = "hypothalamus" )
d2 <- sexbarplots(pitsex, 0, 7000) + labs(subtitle = "pituitary" ) + 
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), axis.ticks = element_blank())
d3 <- sexbarplots(gonsex, 0, 7000) + labs(subtitle = "gonads" ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), axis.ticks = element_blank())

e <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + 
  labs(x = NULL, subtitle = "hypothalamus")  + 
  facet_wrap(~sex, scales = "free")

g <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + 
  labs(x = NULL, subtitle = "pituitary") + 
  facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank())

i <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + 
   facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank()) +
  labs(x = "tSNE1 \n \n \n \n", subtitle = "gonads")

# hyp
f <- makebargraph("hypothalamus","DEGs", 0, 4300) + 
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank())  +
  labs(subtitle = "hypothalamus")
# pit
h <- makebargraph("pituitary","DEGs", 0, 4300)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  +
  labs(subtitle = "pituitary")
# gon
j <- makebargraph("gonad","DEGs", 0, 4300) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabels)+
  labs(subtitle = "gonads")

bcd <- plot_grid(b,c,d1,d2,d3, nrow = 1, labels = c("B", "C", "D"), 
                   label_size = 8, rel_widths = c(1.2,1.2,1.2,1,1))

etoj <- plot_grid(e,f,g,h,i,j, ncol = 2, rel_heights = c(1,1,1.4), rel_widths = c(2.4,3.2),
                  labels = c("E", "F", "G", "H", "I", "J"), label_size = 8)

fig1 <- plot_grid(a, bcd, etoj, nrow = 3, rel_heights = c(0.8,0.7,2),
                  labels = c("A"), label_size = 8)
fig1
```
